Study 2 Analysis

### 2025-01-04 nb/study2.qmd
add s2 demo extras

s2 <- haven::read_sav(here::here("data/Frequency & Probability Study 2 - 3-24-19.sav"))
s2 <- s2 |> #mutate(id = as.numeric(format(EndDate, "%H%M%S"))) |> relocate(id) |> 
  mutate(id=paste0("s2_",row_number())) |> relocate(id)
s2 <- s2 |> filter(!(id=="s2_78")) |> # NA for some responses
  filter(!(id=="s2_196")) # NA for state_avg for COL HEAT - (HEATSTATE2)
  # filter(!(id=="s2_208")) # NA for response for California not rounded Total (TOTALAPONE1 and TOTALAPTWO1) - leave them in since all the acutal app values are okay
s2 <- s2 |> 
  mutate(
    state1 = case_when(
      COLORADO == 1 ~ "Colorado",
      MASSACHUSETTS == 1 ~ "Massachusetts",
      CALIFORNIA == 1 ~ "California",
      TEXAS == 1 ~ "Texas",
      TRUE ~ NA_character_
    ),
    state2 = case_when(
      COLORADO == 2 ~ "Colorado",
      MASSACHUSETTS == 2 ~ "Massachusetts",
      CALIFORNIA == 2 ~ "California",
      TEXAS == 2 ~ "Texas",
      TRUE ~ NA_character_
    )
  ) |> 
  mutate(refClass = case_when(
  REFERENCECLASS == 1 ~ "USD",
  REFERENCECLASS == 2 ~ "kWh",
  REFERENCECLASS == 3 ~ "Percentage"
)) |> 
  rename(calc=MATH01) |>  # replace NA's in calc with 0's
  mutate(calc=factor(ifelse(is.na(calc),0,calc))) |> 
  mutate(calc = if_else(calc == 0, "No Calculator", "Calculator")) |> 
  relocate(refClass,state1,state2,calc, .after = id)

s2 <- s2 |> rename(edu=DEM04) |>
  mutate(edu = factor(case_when(
    edu == '1' ~ "Some schooling, but no diploma or degree",
    edu == 2 ~ "Highschool diploma or GED",
    edu == 3 ~ "Some college",
    edu == 4 ~ "College degree",
    edu == 5 ~ "Some graduate school",
    edu == 6 ~ "Graduate degree",
    edu == 7 ~ "Choose not to answer",
    TRUE ~ NA_character_
  ))) |> relocate(edu, .after = id)

@@

s2_b1 <- s2 |> select(id,state1,refClass,TENPERCENT,ROUNDED, calc, edu,ACFAMILY1:TOTALAPTWO1) |> 
  mutate( 
    block = 1,
    state=state1,
  pct_goal=case_when (TENPERCENT == 1 ~ "10%", TENPERCENT == 2 ~ "15%"), 
  pct=case_when (TENPERCENT == 1 ~ .10, TENPERCENT == 2 ~ .15),
  rounded = case_when(ROUNDED == 1 ~ "Rounded", ROUNDED == 2 ~ "Not Rounded")
  ) |> relocate(id,block,refClass,pct_goal,rounded,state)  |> 
  select(-TENPERCENT,-ROUNDED, -state1)

s2_b2 <- s2 |> select(id,state2,refClass,TENPERCENT,ROUNDED, calc,edu,ACFAMILY2:TOTALAPTWO2) |> 
  mutate( 
    block = 2,
    state=state2,
  pct_goal=case_when (TENPERCENT == 1 ~ "15%", TENPERCENT == 2 ~ "10%"), 
  pct=case_when (TENPERCENT == 1 ~ .15, TENPERCENT == 2 ~ .10),
  rounded = case_when(ROUNDED == 1 ~ "Not Rounded", ROUNDED == 2 ~ "Rounded")
  ) |> relocate(id,block,refClass,pct_goal,rounded,state) |> 
  select(-TENPERCENT,-ROUNDED, -state2)

>>>>

s2 <- haven::read_sav(here::here("data/Frequency & Probability Study 2 - 3-24-19.sav"))
s2 <- s2 |> #mutate(id = as.numeric(format(EndDate, "%H%M%S"))) |> relocate(id) |> 
  mutate(id=paste0("s2_",row_number())) |> relocate(id)
s2 <- s2 |> filter(!(id=="s2_78")) |> # NA for some responses
  filter(!(id=="s2_196")) # NA for state_avg for COL HEAT - (HEATSTATE2)
  # filter(!(id=="s2_208")) # NA for response for California not rounded Total (TOTALAPONE1 and TOTALAPTWO1) - leave them in since all the acutal app values are okay
s2 <- s2 |> 
  mutate(
    state1 = case_when(
      COLORADO == 1 ~ "Colorado",
      MASSACHUSETTS == 1 ~ "Massachusetts",
      CALIFORNIA == 1 ~ "California",
      TEXAS == 1 ~ "Texas",
      TRUE ~ NA_character_
    ),
    state2 = case_when(
      COLORADO == 2 ~ "Colorado",
      MASSACHUSETTS == 2 ~ "Massachusetts",
      CALIFORNIA == 2 ~ "California",
      TEXAS == 2 ~ "Texas",
      TRUE ~ NA_character_
    )
  ) |> 
  mutate(refClass = case_when(
  REFERENCECLASS == 1 ~ "USD",
  REFERENCECLASS == 2 ~ "kWh",
  REFERENCECLASS == 3 ~ "Percentage"
)) |> 
  rename(calc=MATH01, 
         gender=DEM01,
         byear=DEM02,
         edu=DEM04) |> 
  mutate(duration=as.numeric(difftime(lubridate::as_datetime(EndDate), lubridate::as_datetime(StartDate), units = "secs")),
  age=as.numeric(format(StartDate, "%Y")) - byear) |> 
  mutate(edu = factor(case_when(
    edu == '1' ~ "Some schooling, but no diploma or degree",
    edu == 2 ~ "Highschool diploma or GED",
    edu == 3 ~ "Some college",
    edu == 4 ~ "College degree",
    edu == 5 ~ "Some graduate school",
    edu == 6 ~ "Graduate degree",
    edu == 7 ~ "Choose not to answer",
    TRUE ~ NA_character_
  ))) |> 
  mutate(gender = factor(gender, 
                      levels = c(1,2,3),
                      labels = c("Male", "Female", "Not specified"))) |> 
  mutate(calc=factor(ifelse(is.na(calc),0,calc))) |>  # replace NA's in calc with 0's
  mutate(calc = if_else(calc == 0, "No Calculator", "Calculator")) |> 
  relocate(refClass,state1,state2,calc,gender,age,byear,edu,duration, .after = id)

@@

s2_b1 <- s2 |> select(id,state1,refClass,TENPERCENT,ROUNDED, calc,age,gender,edu,duration,ACFAMILY1:TOTALAPTWO1) |> 
  mutate( 
    block = 1,
    state=state1,
  pct_goal=case_when (TENPERCENT == 1 ~ "10%", TENPERCENT == 2 ~ "15%"), 
  pct=case_when (TENPERCENT == 1 ~ .10, TENPERCENT == 2 ~ .15),
  rounded = case_when(ROUNDED == 1 ~ "Rounded", ROUNDED == 2 ~ "Not Rounded")
  ) |> relocate(id,block,refClass,pct_goal,rounded,state)  |> 
  select(-TENPERCENT,-ROUNDED, -state1)

s2_b2 <- s2 |> select(id,state2,refClass,TENPERCENT,ROUNDED,calc,age,gender,edu,duration,ACFAMILY2:TOTALAPTWO2) |> 
  mutate( 
    block = 2,
    state=state2,
  pct_goal=case_when (TENPERCENT == 1 ~ "15%", TENPERCENT == 2 ~ "10%"), 
  pct=case_when (TENPERCENT == 1 ~ .15, TENPERCENT == 2 ~ .10),
  rounded = case_when(ROUNDED == 1 ~ "Not Rounded", ROUNDED == 2 ~ "Rounded")
  ) |> relocate(id,block,refClass,pct_goal,rounded,state) |> 
  select(-TENPERCENT,-ROUNDED, -state2)
